An Invariant Framework for Conducting Reproducible Computational Science

### 2015-03-31 evaluation.tex
Submit version

\begin{table}
\small
    \centering
    \begin{tabular}{lcccr}
    \hline
    \bf Application & \bf Packaging Tool & \bf Obtain Namelist & \bf Create Package & \bf Re-Run (Tool/Time)\\ \hline
	Athena & Parrot & 10 min 14 sec & 00 min 53 sec & Parrot / 09 min 14 sec  \\ \hline
	Athena & PTU & --- & 08 min 48 sec & PTU / 07 min 21 sec  \\ \hline
	TauRoast & Parrot & 22 min 50 sec  & 04 min 25 sec &chroot / 10 min 24 sec \\ \hline
	TauRoast & PTU & --- & 23 min 30 sec & PTU / 08 min 40 sec \\ \hline 
    \end{tabular}
    \normalsize
    \caption{Time Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

>>>>

\begin{table}
\small
    \centering
    \begin{tabular}{ccccr}
    \hline
    \bf Application & \bf Packaging & \bf Obtain	& \bf Create & \bf Re-Execution \\
	\bf Name		& \bf Tool		& \bf Namelist	& \bf Package& \bf (Tool / Time) \\ \hline
	Athena & Parrot & 10 min 14 sec & 00 min 53 sec & Parrot / 09 min 14 sec  \\ \hline
	Athena & PTU & --- & 08 min 48 sec & PTU / 07 min 21 sec  \\ \hline
	TauRoast & Parrot & 22 min 50 sec  & 04 min 25 sec &chroot / 10 min 24 sec \\ \hline
	TauRoast & PTU & --- & 23 min 30 sec & PTU / 08 min 40 sec \\ \hline 
    \end{tabular}
    \normalsize
    \caption{Time Comparison between Parrot and PTU}
    \label{table:parrot_ptu}
\end{table}

### 2015-03-31 tauroast.tex
Submit version

Code and data in \emph{TauRoast} are available through five different networked filesystems which are mounted locally, an HDFS cluster for data, 
some configuration files were stored on CVMFS~\cite{blomer2011cernvm}, and a variety of software tools were on an NFS, PanFS and AFS systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}. 
\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}
Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the topic of research. Similarly the software may name many possible components but the used components are
smaller than the named ones.

>>>>

Code and data in \emph{TauRoast} are available through five different networked filesystems which are mounted locally, an HDFS cluster for the CMS dataset, 
some configuration files were stored on CVMFS~\cite{blomer2011cernvm}, and a variety of software tools were on an NFS, PanFS and AFS systems.
In addition, code may exist in version control systems such as Git, CVS, and CMS Software Distribution (CMSSW). %~\cite{cms2006cms}.

\begin{wrapfigure}{r}{0.4\textwidth}
\small
\centering
\includegraphics[width=.4\textwidth]{data-code-size.eps}
\caption{Inputs to Tau Roast}
\label{fig:data-code-size}
\end{wrapfigure}

Data that is input to \emph{TauRoast} is obtained by reducing it through a pipeline, as shown in Figure \ref{fig:data-code-size}. Consequently, the real input data may 
vary depending upon the topic of research. Similarly the software may name many possible components but the used components are
smaller than the named ones.
